---
title: "PATRIC Design 4"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
ggplot2::theme_set(ggplot2::theme_bw())
ggplot2::theme_update(text = element_text(size = 10))
ggplot2::theme_update(legend.position = "top")
# ggplot2::theme_update(legend.title = element_blank())
ggplot2::theme_update(axis.text.x = element_text(size = 10))
ggplot2::theme_update(axis.text.y = element_text(size = 10))


estBetaParams <- function(mu, sd) {
  var = sd^2
  
  if(mu < 0.00001 | mu > 0.99999) return(NA)
  if(var < 0.00001 | var > 0.24999) return(NA)
  
  alpha <- ((1 - mu) / var - 1 / mu) * mu ^ 2
  beta <- alpha * (1 / mu - 1)
  return(params = list(alpha = alpha, beta = beta))
}

l1 <- estBetaParams(0.8, 0.05)
l2 <- estBetaParams(0.75, 0.05)

y1 <- rbeta(1000, l1$alpha, l1$beta)
y2 <- rbeta(1000, l2$alpha, l2$beta)

d1 <- density(y1)
d2 <- density(y2)

d3 <- density(y1-y2)

ymax <- max(c(d1$y, d2$y))
xlim <- range(d1$x, d2$x)

plot(d3)

plot(d1)




drc_true_mu <- function(x){
  
  # p_rec <- p_range * pnorm(dose, location, scale) + p_lwr
  
  
  p_rec <- pgrid$p_range[x] * pnorm(dose, 
                                    pgrid$location[x], 
                                    pgrid$scale[x]) + pgrid$p_lwr[x]

  return(p_rec)
  
}

```

# Design 4

Looking at association between dose (duration of antibiotic treatment) and response (recovery by 7 days).
Time to recovery is another option for the endpoint.

Previously, multi-bottle stratergy proposed examining non-inferiority between SOC and comparator durations.
Durations and NI thresholds would, to all intents and purposes, be selected arbitrarily.
Pichichero (2010) provides commentary on durations - 10 days is not unusual globally so we should include to improve generalisability.

*Contention*   

*Plausible is a scenario whereby a 7 day duration is superior to a 3 day duration, but equivalent to a 4 day duration.*
*If our selected durations are $a$ and $b$ with $a < b$, we have no information regarding the profile of the duration-response curve over $(a, b)$ and therefore no ability to compare any of $a + \Delta$ versus $b$ for $\Delta < b - a$.*

Pouwels (2019) strongly suggests duration-response evaluation as a way to optimise antibiotic duration.
Approaches have been suggested in the literature to assess treatment duration including adaptive designs, e.g. RAR, play-the-winner, drop-the-loser.
Quartagno et al (2018) suggests a fixed design with a focus on gaining information to model the duration-response relationship over a pre-specified range. 
They evaluate sensitivity to key design parameters, including sample size, number and position of arms, ultimately recommending approx. 500 patients to 5 to 7 arms.

## Proposed Design

No blinding. 
No rescue. 
Let $T_d$ be a treatment duration in days with $d \in {0, 1, \dots, 10}$ and $\pi_d$ be the proportion recovered by day 7 under treatment $T_d$.
Let $\delta_{ji} = \pi_j - \pi_i$ with $j > i$ and let $\gamma$ be some fixed non-inferiority threshold, e.g. 5%.
Treatments are randomised (with fixed allocation).
No arm-dropping in this design, although it could be used to increase efficiency.
Examine:

+ superiority: $Pr(\pi_j > \pi_i) > \zeta_s$   for $j = max(d)$ and $j > i$
+ NI: $Pr(\delta_{ji} < \gamma) > \zeta_n$ for $j = max(d)$ and $j > i$

Test both against some calibrated probability threshold, e.g. $\zeta_i = 0.9$.

In English, test (1) probability that recovery in the maximum dose is higher than all others, (2) probability mass of the difference is within some non-inferiority threshold e.g. 5%, 10%.
Tests could be extended to all pairwise differences.

Issues/comments:

1. No blinding - in practice, seems like blinding might complicate statistics and challenge logistics to little quantifiable gain.
2. Fixed allocation - in RAR, interim results may influence clinicians and lead to selection bias.
3. Assuming monotone functions for dose might be reasonable.

Questions:

1. Is relapse at day $x$ a worthwhile/relevant consideration?
2. Are there known host by pathogen interactions, e.g. patient characteristics that lead to variations in optimal duration?
3. Consider background changes in the population response to antibiotics?
4. Model non-compliance - here non-compliance can result in non-conservative distortion of conclusions. Hernan (2017) talks about this. Argument is that this is pragmatic study.

## Data Generation

Figure 1 shows a number of possible dose profiles.
Each scenario comprises 11 distinct treatment durations $T_d$ with $d \in \{0, 1, \dots, 10\}$.

```{r, echo = F, fig.width=5.5, fig.height=5.5, fig.cap="Some data generation scenarios"}

dose <- 0:10

pgrid <- expand.grid(location = c(3, 5, 7),
                     scale = c(0.2, 1.2, 3),
                     p_range = c(0, 0.1, 0.3),
                     p_lwr = 0.5)
pgrid$id <- as.character(paste0("V", rep(1:nrow(pgrid))))


m <- do.call(rbind, lapply(1:nrow(pgrid), drc_true_mu))
dfig <- as.data.frame(t(m)) %>%
  tidyr::gather("id", "mu") %>%
  dplyr::mutate(dose = rep(dose, len = length(dose)*nrow(pgrid)))

dfig <- merge(dfig, pgrid, by = "id")

ggplot(dfig, aes(dose, mu, group = id))+
  geom_line() +
  geom_point(size=0.4) +
  scale_y_continuous("Pr(recov)", lim = 0:1) +
  scale_x_continuous("Days", breaks = c(0, 2, 4, 6, 8, 10)) +
  facet_grid(paste0("Mean ", location) ~ paste0("Pr. range ", p_range ))
```

\newpage



# Dynamic state space model

Berry (2010) and Pouwels (2019) refer to a dynamic linear model, a form of state space model, for dose-response. We take an analogous approach as a modelling strategy. We estimate the log-odds of the first dose independently and then the cumulative differences under a random walk. The model reflects some underlying state that varies according to a random walk, which we observe with noise. In notation, let $\eta_j$ denote the log-odds at dose $d \in D_j$, $j = 1, 2, \dots, J$. We formulate a model which locally fits a level for the proportion recovered at each dose. If we let $y_{j}$ be the number of events occurring at dose $j$, we have:

\begin{align*}
y_{j} &\sim \text{Bin}(n_j, \text{logit}^{-1}(\eta_j))   \\ 
\tau_0 &\sim \text{Student\_t}_+(3, 0, 2.5)     \\  
\tau &\sim \text{Student\_t}_+(3, 0, 2.5)     \\ 
\eta^*_{[1]} &\sim N(0, \tau_0)   \\ 
\eta^*_{[2:J]} &\sim N(0, \tau)   \\ 
\eta_j &= \eta^*_{[1]} + \sum_{j=2}^J \eta^*_{j}
\end{align*}

The model amounts to estimating a reference chance of recovery on the logit scale and then the deviations from that reference as a random walk.
The attraction is that it does not enforce arbitrary parameteric assumptions about the shape of the dose response curve.
To allow for non-unit increments in the dosage, simply scale the variance of the state model by the difference between successive doses.
















