---
title: "PATRIC Simulation Results"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(kableExtra))
suppressPackageStartupMessages(library(psych))
suppressPackageStartupMessages(library(grid))
suppressPackageStartupMessages(library(gridExtra))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(htmltools))


ggplot2::theme_set(ggplot2::theme_bw())
ggplot2::theme_update(text = element_text(size = 10))
ggplot2::theme_update(legend.position = "top")
# ggplot2::theme_update(legend.title = element_blank())
ggplot2::theme_update(axis.text.x = element_text(size = 10))
ggplot2::theme_update(axis.text.y = element_text(size = 10))


source("report_util.R")

```

```{r, include=FALSE}



lres <- load_results_data("out05c")



```



## Recovering Parameters

```{r, echo = F, eval = T}
digits <- c(0, 2, 0, 2, 2, 0, 0, 0, 0,
            rep(2, unique(lres$drecov$n_doses))
            )

comparison_names <- paste0(lres$doses, " days")

kable(lres$drecov,
      caption = paste0("Table. Simulation Results (", nrow(lres$drecov), " rows)"),
      col.names = c("Scenario", "Range", "mid", "lwr", "upr", "n(dose)", "min(dose)", "max(dose)",  "n_per_arm", 
                    comparison_names),
      digits = digits) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = F, position = "left",
                font_size = 12,
                latex_options = "hold_position") 

```

The figure below shows the estimated (black) proportion recovered by the model.

```{r, echo = F, fig.width=5.5, fig.height=3.5, fig.cap="Estimated and true probability of recovery (error bar from 0.1 to 0.9 quantile)", fig.align="center"}

dfig1 <- lres$drecov %>%
  dplyr::select(-max_dose, -min_dose, -n_doses, -mu_lwr, -mu_upr) %>%
  tidyr::gather("dose", "precov", -range, -scenario, -n_per_trt, -mid) %>%
  dplyr::arrange(scenario, dose) %>%
  dplyr::mutate(dose = gsub("D", "", dose), 
    dose = as.numeric(dose))

dfig1_lwr <- lres$drecov_lwr %>%
  dplyr::select(-max_dose, -min_dose, -n_doses, -mu_lwr, -mu_upr) %>%
  tidyr::gather("dose", "precov", -range, -scenario, -n_per_trt, -mid) %>%
  dplyr::arrange(scenario, dose) %>%
  dplyr::mutate(dose = gsub("D", "", dose), 
    dose = as.numeric(dose)) %>%
  dplyr::select(scenario, dose, precov) %>%
  dplyr::rename(precov_lwr = precov)

dfig1_upr <- lres$drecov_upr %>%
  dplyr::select(-max_dose, -min_dose, -n_doses, -mu_lwr, -mu_upr) %>%
  tidyr::gather("dose", "precov", -range, -scenario, -n_per_trt, -mid) %>%
  dplyr::arrange(scenario, dose) %>%
  dplyr::mutate(dose = gsub("D", "", dose), 
    dose = as.numeric(dose)) %>%
  dplyr::select(scenario, dose, precov) %>%
  dplyr::rename(precov_upr = precov)

dfig1 <- merge(dfig1, dfig1_lwr, by = c("scenario", "dose"))
dfig1 <- merge(dfig1, dfig1_upr, by = c("scenario", "dose"))


ggplot(dfig1, aes(x = dose, y = precov, group = scenario))+
  geom_line() +
  geom_errorbar(aes(ymin = precov_lwr , ymax = precov_upr), width = 0.0) + 

  # geom_point(data = dtrue_mu, 
  #   aes(x = dose, y = true_mu, group = scenario), col = "red") +
  scale_y_continuous("Pr(recov)", lim = 0:1) +
  scale_x_continuous("Days", breaks = c(0, 2, 4, 6, 8, 10)) +
  facet_grid(paste0("Mid-point ", mid )~ paste0("Pr. range ", range ))

```




## Bias

```{r, echo = F, eval = T}
digits <- c(0, 2, 0, 2, 2, 0, 0, 0, 0, 
            rep(2, unique(lres$drecov$n_doses))
            )

comparison_names <- paste0(lres$doses, " days")

kable(lres$dbias,
      caption = paste0("Table. Simulation Results (", nrow(lres$dbias), " rows)"),
      col.names = c("Scenario", "Range", "mid", "lwr", "upr", "n(dose)", 
                    "min(dose)", "max(dose)",  "n_per_arm", 
                    comparison_names),
      digits = digits) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = F, position = "left",
                font_size = 12,
                latex_options = "hold_position") 

```


## Superiority

The columns with "10 Days versus x days" show the proportion of times that the probability of recovery on the maximum duration antibiotic was found to be higher than the probability of recovery on the 1 day, 2 days, 3 days etc. In these examples we used a 90% decision threshold, i.e. those with $Pr(\pi_{max(d)} > \pi_i) > 0.9$ where $\pi_k$ is the probability (or proportion) recovered on dose $d$ and $d \in \{0, 1, \dots, 5\}$.

Range gives the range in underlying true recovery probability with a lower bound of 0.5 in all scenarios. For example, a range equal to 0.3 implies that we generate data from parameter values from 0.5 to 0.8.


```{r, echo = F, eval = T}
digits <- c(0, 2, 0, 2, 2, 0, 0, 0, 0, 
            rep(2, unique(lres$drecov$n_doses)-1)
            )

comparison_names <- paste0(lres$doses[-length(lres$doses)], " days")

kable(lres$dsup,
      caption = paste0("Table. Simulation Results (", nrow(lres$dsup), " rows)"),
      col.names = c("", "", "", "lwr","upr","doses", "min", "max", "n_per_trt",
                    comparison_names),
      digits = digits) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = F, position = "left",
                font_size = 12,
                latex_options = "hold_position")  %>%
  add_header_above(c("Scenario" = 1, "Range" = 1, 
                     "Mid" = 1, 
                     "Pr(recov)" = 2,
                     "N"=1, "Dose"=2, 
                     "N" = 1,
    "Max duration versus" = lres$n_doses-1))

```

## Non-inferiority

Analogous to above but here we examine non-inferiority. NI is determined by setting an NI margin and making a decision based on the distribution of difference between proportions is above this NI margin. See design doc for further explanation.

Here we show proportion of times that the probability of recovery ont the 1 day, 2 days, 3 days ... arms was found to be NI to the probability of recovery on the maximum duration arm.

We used a 5% NI margin and a 60% decision threshold. 


```{r, echo = F, eval = T}
digits <- c(0, 2, 0, 2, 2, 0, 0, 0, 0, 
            rep(2, unique(lres$drecov$n_doses)-1)
            )

comparison_names <- paste0(lres$doses[-length(lres$doses)], " days")

kable(lres$dni,
      caption = paste0("Table. Simulation Results (", nrow(lres$dni), " rows)"),
      col.names = c("", "", "", "lwr","upr","doses", "min", "max", "n_per_trt",
                    comparison_names),
      digits = digits) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = F, position = "left",
                font_size = 12,
                latex_options = "hold_position")  %>%
  add_header_above(c("Scenario" = 1, "Range" = 1, 
                     "Mid" = 1, 
                     "Pr(recov)" = 2,
                     "N"=1, "Dose"=2, 
                     "N" = 1,
    "Max duration versus" = lres$n_doses-1))




```


## Todo

