---
title: "PATRIC"
date: "`r Sys.time()`"
output:
  html_document:
    classoption: portrait
    number_sections: no
    self_contained: yes
    theme: united
  pdf_document:
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_depth: 3
  word_document:
    toc: yes
    toc_depth: '3'
geometry: left=0.2cm,right=0.2cm,top=1cm,bottom=1cm
editor_options:
  chunk_output_type: console
classoption: landscape
---
<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r setup, include=FALSE}
# rmarkdown::render("simulation_report.Rmd", clean=TRUE)
knitr::opts_chunk$set(echo = TRUE, fig.path = 'figs/')
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(kableExtra))
suppressPackageStartupMessages(library(psych))
suppressPackageStartupMessages(library(grid))
suppressPackageStartupMessages(library(gridExtra))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(htmltools))
#source("util.R")



ggplot2::theme_set(ggplot2::theme_bw())
ggplot2::theme_update(text = element_text(size = 10))
ggplot2::theme_update(legend.position = "top")
# ggplot2::theme_update(legend.title = element_blank())
ggplot2::theme_update(axis.text.x = element_text(size = 10))
ggplot2::theme_update(axis.text.y = element_text(size = 10))

# Work|Right|Fast
# rmarkdown::render("simulation_report.Rmd", clean=TRUE)
```


```{r, echo = F, include=FALSE}
mywarnings <- list()

post_final_thresh <- 0

resfiles <- list.files("out", pattern = "*.RDS")

df_all <- data.frame(stringsAsFactors = F)

mysim <- 1
# fname = resfiles[1]
for(fname in resfiles){
  
  l1 <- readRDS(file.path(getwd(), "out", fname))
  # d1 <- readRDS(file.path(getwd(), "out", resfiles[1]))

  df_res <- as.data.frame(l1$results)

  # true values for median surv (mnth)
  true_mean <- l1$trtgrps$true_mean
  names(true_mean) <- as.character(l1$trtgrps$grplab)
  prop_rescue  <- l1$trtgrps$prop_rescue
  names(prop_rescue) <- as.character(l1$trtgrps$grplab)
  est_prob  <- l1$trtgrps$est_prop
  names(est_prob) <- as.character(l1$trtgrps$grplab)
  

  mean(df_res$mean_a_diff > 0)
  mean(df_res$mean_p_diff > 0)
  mean(df_res$mean_diff_in_diff > 0)
  
  mean(df_res$a3_ni_a5)
  mean(df_res$p3_ni_p5)
  mean(df_res$a_eq_p)
  
  dtmp <- t(cbind(c(true_mean, prop_rescue, est_prob)))
  
  scen <- ifelse(is.null(l1$scenario), NA, l1$scenario)
  
  dtmp <- cbind(dtmp, 
                a3_gt_a5 = mean(df_res$mean_a_diff > 0),
                p3_gt_p5 = mean(df_res$mean_p_diff > 0),
                diff_a_gt_diff_p = mean(df_res$mean_diff_in_diff > 0),
                a3_ni_a5 = mean(df_res$a3_ni_a5),
                p3_ni_p5 = mean(df_res$p3_ni_p5),
                a_eq_p = mean(df_res$a_eq_p),
                scenario = scen)

  df_all <- rbind(df_all,  dtmp, stringsAsFactors  = F)

}


options(knitr.kable.NA = '-')
showwarn <- length(mywarnings > 0)

#max_file_date <- as.POSIXct("2019-03-13 23:11:48")

```

## Design 2

Each participant receives a bottle containing one of 5 days antibiotic, 3 days antibiotic, 5 days placebo or 3 days placebo. 

All receive a prescription for rescue medication, which could be obtained at any time. 

We would know that the prescription had been filled (and the date at which it was filled) but we would not know whether it was taken or whether a full dose had been taken.

If a participant reaches for the rescue medication (regardless of whether they are on the active or placebo arms) they are considered a failure, i.e. considered that they had not recovered at day 7 regardless of whether they did or did not.

Initially am using a non-inferiority margin equal to 0.05, equivalence 0.05. 

The decision thresholds for NI is 0.9 and equivalence is 0.6.


## Results and commentary

In scenario 4 all arms have a true recover probability of 0.7. Patients on the 3 day regimes are assumed to jump to rescue sooner and therefore in aggregate more people in the 3 day duration jump to rescue. Since people who jump to rescue are considered failures, we anticipate that we would see (and estimate) that proportion that recovered in the 3 day regimes would be lower than the proportion recovered in the 5 day regimes. The simulation results confirms that this is the case. The implications include (1) the probability that day 3 regimes are greater than day 5 regimes is negligible (2) the probability that day 3 regimes are non-inferior to day 5 regimes is negligible, and (3) the probability that the difference between the active arms and the difference between the placebo are equivalent is quite high.


```{r, echo = F}
digits <- c(rep(3, 14))
kable(df_all,
      caption = paste0("Table. Simulation Results (", nrow(df_all), " rows)"),
      col.names = c("A5", "A3", "P5", "P3", 
                    "A5", "A3", "P5", "P3", 
                    "A5", "A3", "P5", "P3", 
                    "",
                    "",    
                    "",
                    "",
                    "",
                    "",
                    ""),
      digits = digits) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = F, position = "left",
                font_size = 12,
                latex_options = "hold_position") %>%
  add_header_above(c("True recovery" = 4, 
                     "True rescue" = 4, 
                     "Est. recovery" = 4, 
                     "P(a3 gt a5)" = 1, 
                     "P(p3 gt p5)" = 1, 
                     "P(d1 > d0)" = 1, 
                     "P(a3 ni a5)" = 1,
                     "P(p3 ni p5)" = 1,
                     "P(d1 eq d0)" = 1,
                     "Scenario"    = 1))
```











